Title

### 2012-03-16 inc/magnetic_lenses/maglens.tex
update magnetic lens numbers because my notes were incorrect

%TODO check S and D as I seem to remember we have S=0.1in
%TODO need a description of the steel inner tube causing an effective diameter larger than the actual bore
For the UEM, I chose a bore diameter $D$=0.3in and a pole-piece gap $S$=0.5in, for an ratio $S/D=0.6$.
By their table 8.2a this results in $\beta=0.0104$. Then, to create a focal length of 4in ($f/R=16$) table 8.17 gives a value for $k^2 \approx 0.05$.
Finally substituting this value into \ref{eq:elkareh_k2}, with $V=30$kV ($V_r\approx30.88$kV), one can deduce that $NI\approx385$A.

To further ease the burden on the lenses, I actually created two, one placed to either side of the RF cavity. As each has 100 turns, a current of only 2A is needed to drive the two lenses in series.

>>>>

%TODO check S and D as I seem to remember we have S=0.1in
%TODO need a description of the steel inner tube causing an effective diameter larger than the actual bore
For the UEM, I chose a bore diameter $D=2R=$0.1in and a pole-piece gap $S$=0.5in, for an ratio $S/D=0.2$.
By their table 8.2a this results in $\beta=0.0146$. Then, to create a focal length of 4in ($f/R=16$) table 8.13 gives a value for $k^2 \approx 0.06$.
Finally substituting this value into \ref{eq:elkareh_k2}, with $V=30$kV ($V_r\approx30.88$kV), one can deduce that $NI\approx356$A.

To further ease the burden on the lenses, I actually created two, one placed to either side of the RF cavity. As each has 100 turns, a current of only 2A is needed to drive the two lenses in series. The oxygen-free copper wire coils remain cool to the touch under these operating conditions.
